IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2015-01-15 paper/conclusion.tex
pass over related and conclusion

In this paper, we argued that when designing a coarse-grained IFC
system, it is better to start with a fully isolated, multi-task system
and work one's way back to the model of a single language equipped
with IFC.  We showed
how systems designed this way can be proved non-interferent
without needing to rely on details of the target language, and
we provided conditions on how to securely refine our formal semantics to
consider optimizations required in practice.  We connected our semantics
to two IFC implementations for JavaScript based on this formalism,
explained how our methodology improved an exiting IFC system for Haskell,
and proposed
an IFC system for C using hardware isolation.
By systematically applying ideas from IFC in operating systems to programming languages,
we hope to have elucidated some of the core design principles of coarse-grained,
dynamic IFC systems.

>>>>

In this paper, we argued that when designing a coarse-grained IFC
system, it is better to start with a fully isolated, multi-task system
and work one's way back to the model of a single language equipped
with IFC.  We showed
how systems designed this way can be proved non-interferent
without needing to rely on details of the target language, and
we provided conditions on how to securely refine our formal semantics to
consider optimizations required in practice.  We connected our semantics
to two IFC implementations for JavaScript based on this formalism,
explained how our methodology improved an exiting IFC system for Haskell,
and proposed
an IFC system for C using hardware isolation.
By systematically applying ideas from IFC in operating systems to
programming languages for which isolation can be achieved,
we hope to have elucidated some of the core design principles of coarse-grained,
dynamic IFC systems.

### 2015-01-15 paper/related.tex
pass over related and conclusion

One information flow control technique designed to handle legacy code is
secure multi-execution (SME)~\cite{Devriese:2010}. It runs
multiple copies of the program, one per security level, where the semantics of
I/O interactions is altered. Authors often present
SME considering one specific programming
language~\cite{KULeuven-350547,Rafnson:2013}. However, Bielova et
al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
details of the underlying language is hidden.  Zanarini et
al.~\cite{ZanariniJR13} propose a novel semantics for programs based on
interaction trees~\cite{jacobs-tutorial}, which treats programs as black-boxes
about which nothing is known except what is inferred from their I/O interactions
with the environment. Similar to SME, our approach mediates I/O
operations; however, our approach only runs the program once.

One of the primary motivations behind this paper is constructing a practical
information flow control system for JavaScript.  Some of these systems attempt
to perform fine-grained information flow control of
JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
control can result in fewer false alarms and target legacy code, it comes at the
cost of complexity (the system must accommodate the entirety of JavaScript's
semantics~\cite{JSFlow}).
%Moreover, the runtime performance cost are sometimes too high, e.g.,
%higher than 100\%~\cite{JSFlow}.
Alternatively, coarse-grained
approaches to security have also been proposed for the web
scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.

@@

The constructs in our IFC language, as well as the behavior of
inter-thread communication, are reminiscent of distributed systems
like Erlang~\cite{Armstrong03makingreliable}.  There is a close
correspondence: in distributed systems, isolation is required due to
physical constraints; in information flow control, isolation is
required to enforce noninterference.  Papagiannis et al.~\cite{Papagiannis_enforcinguser}
built an information flow control system on top of Erlang which is quite
similar to ours.  However, they do not use a floating label system (processes
can find out when sending a message failed due to a forbidden information flow),
and they include no security proofs.

There appears to be limited literature in general techniques for retrofitting
information flow control to arbitrary languages; however, one time-honored
technique is defining a fundamental calculus, for which other languages can be
desugared into.  Abadi et al.~\cite{abadi+:core} motivate their core calculus of
dependency by showing how various previous systems can be encoded in it; Tse and
Zdancewic~\cite{Tse:Zdancewic:ICFP04}, in turn, show how this calculus can be
encoded in System F via parametricity.  Broberg and Sands~\cite{Broberg:2010}
encode several IFC systems into Paralocks.  However, this line of work is
primarily focused on static enforcements.
%information flow control systems.

>>>>

One information flow control technique designed to handle legacy code is
secure multi-execution (SME)~\cite{Devriese:2010}. SME runs
multiple copies of the program, one per security level, where the semantics of
I/O interactions is altered. Authors often present
SME in the context of a single, specific programming
language~\cite{KULeuven-350547,Rafnson:2013}. However, Bielova et
al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
details of the underlying language are hidden.  Zanarini et
al.~\cite{ZanariniJR13} propose a novel semantics for programs based on
interaction trees~\cite{jacobs-tutorial}, which treats programs as black-boxes
about which nothing is known, except what can be inferred from their interaction
with the environment. Similar to SME, our approach mediates I/O
operations; however, our approach only runs the program once.

One of the primary motivations behind this paper is the application of
information flow control to JavaScript.  Previous systems 
retrofitted JavaScript with fine-grained
IFC~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained IFC can result
in fewer false alarms and target legacy code, it comes at the
cost of complexity: the system must accommodate the entirety of JavaScript's
semantics~\cite{JSFlow}.
%Moreover, the runtime performance cost are sometimes too high, e.g.,
%higher than 100\%~\cite{JSFlow}.
By contrast, coarse-grained
approaches to security have also been proposed for the web
scenario and tend to have simpler implications~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.

@@

The constructs in our IFC language, as well as the behavior of
inter-task communication, are reminiscent of distributed systems like
Erlang~\cite{Armstrong03makingreliable}.  There is a close
correspondence: in distributed systems, isolation is required due to
physical constraints; in information flow control, isolation is
required to enforce non-interference.  Papagiannis et
al.~\cite{Papagiannis_enforcinguser} built an information flow control
system on top of Erlang which shares some similarities to ours.
However, they do not take a floating-label approach (processes can find
out when sending a message failed due to a forbidden information
flow), nor do they provide security proofs.

There is limited work on general techniques for retrofitting
arbitrary languages with information flow control. However, one time-honored
technique is to define a fundamental calculus for which other languages can be
desugared into.  Abadi et al.~\cite{abadi+:core} motivate their core calculus of
dependency by showing how various previous systems can be encoded in it. Tse and
Zdancewic~\cite{Tse:Zdancewic:ICFP04}, in turn, show how this calculus can be
encoded in System F via parametricity.  Broberg and Sands~\cite{Broberg:2010}
encode several IFC systems into Paralocks.  However, this line of work is
primarily focused on static enforcements.
%information flow control systems.
